---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shellcheckr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

`shellcheckr` allows you to run [`shellcheck`](https://www.shellcheck.net/) manually or as an [addin](https://rstudio.github.io/rstudioaddins/) when editing shell script files in RStudio.

## Installation

You can install the released version of `shellcheckr` from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("shellcheckr")
```

**NOTE** you must have `shellcheck` in your `$PATH`.

## Example

Normally you would run `shellcheckr` from the *Addins->ShellCheck* toolbar menu item. The main menu *Tools->Modify Keyboard Shortcuts* can be used to make a shortcut for it. You can also call it manually:

```{r example, eval = FALSE}
library(shellcheckr)
shellcheckr('~/.bashrc') # raw JSON output
shellcheckrMarkers('~/.bashrc') # markers with wiki links
```
